### 2019-02-14 sections/intuition.tex
changes to section 3.5

%NOTE: depends on: editors
As users can continuously update editors, tasks never terminate.

>>>>

%NOTE: depends on: editors
Users can continuously interact with tasks, they will never terminate. The event
send by a user leads to a new task that can always receive a new event.

The new task can either be the same task, but with a new value for the changed
editor, or the system can decide to move on to the next task.
